\subsection{Benchmarking the hallucation rate of our model}


After constructing the above mentioned model, we have done extensive benchmarking in order to validate our hallucination rate improvements. For these benchmarks we have chosen the HaluEval 2.0 benchmark \cite{li2024dawn}, which strongly builds on the original HaluEval benchmark paper \cite{li2023halueval}. This benchmark measures the rate of factual and non-factual answers given by a model in the following five domains: Biomedicine, Finance, Science, Education, and Open Domain, comprising a total of 8,770 questions across these domains. These benchmark detects hallucinations in two steps: first extracting factual statements from the model’s responses, and then automatically judging their truthfulness against world knowledge. This method has been validated against human annotation and shown to be highly reliable. Notably, the HaluEval 2.0 benchmark uses two different scores for a model in one domain: MaHR and MiHR. MiHR stands for micro hallucination rate and is calculated in the following way: 
\[
\text{MiHR} = \frac{1}{n} \sum_{i=1}^{n} 
\frac{\text{Count}(\textit{hallucinatory facts})}
{\text{Count}(\textit{all facts in } r_i)},
\]
In the above formula \textit{n} stands for the total number of samples, while $r_i$ is the \textit{i}-th response. The other score, MaHR stands for macro hallucination and is calculated in the following way:
\[
\text{MaHR} = \frac{\text{Count}(\textit{hallucinatory responses})}{n}.
\]
In our tests we compared our own model to some of the current flagship Large Language Models by Meta \cite{Llama}, Mistral \cite{Mistral}, Anthropic \cite{Anthropic}, Google \cite{Gemini} and OpenAI \cite{OpenAI}.
The first three rows of Table~\ref{tab:res} illustrate the progressive effect of our interventions. The \textbf{Base Model}, trained on low-reliability data, shows the highest hallucination rates across all domains. Switching to high-quality corpora (\textbf{Data Improvement}) yields a notable reduction in both MaHR and MiHR, highlighting the strong influence of training data reliability. Finally, our proposed architecture with the Layer-Specific Factual Gate (\textbf{Model Improvement}), trained on the same high-quality data, achieves the lowest hallucination rates overall, demonstrating the combined benefit of clean data and architectural enhancements.



\begin{table}[ht]
\centering
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{1.1}
\footnotesize

\caption{HaluEval 2.0 hallucination rates (MaHR and MiHR) across five domains. Results are shown for our baseline model, data-improved model, and architecture-improved model, against other current flagship LLM models. Lower is better.}
\label{tab:res}

\resizebox{\textwidth}{!}{
\begin{tabular}{lcccccccccc}
\toprule
\multirow{2}{*}{Models} &
\multicolumn{2}{c}{Biomedicine} &
\multicolumn{2}{c}{Finance} &
\multicolumn{2}{c}{Science} &
\multicolumn{2}{c}{Education} &
\multicolumn{2}{c}{Open Domain} \\
\cmidrule(lr){2-3} \cmidrule(lr){4-5} \cmidrule(lr){6-7} \cmidrule(lr){8-9} \cmidrule(lr){10-11}
 & MaHR & MiHR & MaHR & MiHR & MaHR & MiHR & MaHR & MiHR & MaHR & MiHR \\
\midrule
\bfseries \textbf{Base Model}          
  & \textbf{1.92} & \textbf{0.87}  
  & \textbf{1.88} & \textbf{0.79}  
  & \textbf{1.73} & \textbf{0.66}  
  & \textbf{1.95} & \textbf{0.91}  
  & \textbf{1.99} & \textbf{0.98} \\

\bfseries \textbf{Data Improvement}    
  & \textbf{1.21} & \textbf{0.52}  
  & \textbf{1.09} & \textbf{0.48}  
  & \textbf{1.14} & \textbf{0.44}  
  & \textbf{1.28} & \textbf{0.53}  
  & \textbf{1.31} & \textbf{0.59} \\

\bfseries \textbf{Model Improvement}   
  & \textbf{0.44} & \textbf{0.11}  
  & \textbf{0.38} & \textbf{0.09}  
  & \textbf{0.42} & \textbf{0.08}  
  & \textbf{0.47} & \textbf{0.12}  
  & \textbf{0.53} & \textbf{0.14} \\
\midrule
Llama 4            & 28.76 &  7.23 & 35.91 &  9.25 & 15.21 &  3.36 & 36.84 & 10.13 & 39.18 & 12.62 \\
Mistral Large 2.1   & 31.44 &  8.25 & 39.11 & 10.56 & 21.31 &  4.78 & 41.26 & 11.53 & 55.39 & 19.50 \\
Claude Sonnet 4.5   & 34.88 & 15.07 & 41.51 & 18.24 & 29.99 &  9.19 & 37.82 & 17.80 & 44.51 & 25.93 \\
Gemini 2.5 Pro	& 46.38 & 14.27 & 56.01 & 16.65 & 43.11 & 12.11 & 58.86 & 19.54 & 70.53 & 25.25 \\
OpenAI GPT-5        & 14.20 &  3.98 & 20.10 &  5.52 & 11.80 &  3.31 & 24.60 &  6.92 & 27.90 &  8.84 \\
OpenAI GPT-4.1      & 16.80 &  4.62 & 23.40 &  6.41 & 13.60 &  3.87 & 27.80 &  7.85 & 31.80 &  9.96 \\
\bottomrule
\end{tabular}
}
\end{table}

